Cryptographic assurance of secrecy and fairness in voting

### 2012-12-06 paper/paper.tex
Adjust whitespace in \author

Once votes have been collected, it is the responsibility of the state to tally votes for the various
candidates in a race and publish \emph{accurate} tallies. Generally, the electorate is reliant on
\emph{someone} (e.g., the government at some level) to provide these tallies. But it is much less
common for voters themselves to have the opportunity to verify that the votes were tallied
\emph{exactly} as they were cast.

@@

While the notions of verifiability presented above allow one to ensure that votes were counted as
they were cast, another problem is to ensure that the body holding the election cannot fabricate
\emph{additional} votes (not actually cast) to raise the tallies as it sees fit.

@@

Amidst these other goals, it becomes difficult to prevent \term{coercion}: the ability of some party
to coerce (through force, payment, or otherwise) a voter to vote for a particular candidate.

@@

Before an election is held, the body holding the election (e.g., the government) must construct four
Tables that lie at the core of the Scantegrity system: Tables P, Q, R, and S.

Some selection of persons associated with the electing body use a secret-sharing scheme to protect a
secret pseudorandom number generator key. Table P lists every ballot that will be produced for the
election and specifies exactly what code (which we'll see later) is used for each candidate per
ballot. These codes are generated using the pseudorandom generator and \emph{must} be kept secret.

@@

When a ballot has been received, the following takes place:
\begin{enumerate}
	\item
		The candidate code is revealed in Table Q. (If this is an audit ballot -- see below -- then all
		are revealed, and we'll perform the following steps for each code.)
	\item
		A ``check'' is placed on the row in Table R that maps the revealed Q value to some value in S.
	\item
		The Table R mapping is followed into Table S, and a ``check'' is added to a cell in Table R
		(to be counted as a vote for that row's candidate).
\end{enumerate}

@@

Helios \cite{helios} -- unlike Scantegrity and \pv{} -- is an \emph{online} voting
system that attempts to meet many of the same goals (namely, verifiability).

@@

At the heart of Helios is a single ElGamal keypair. The secret key is known only to the Helios
server, but the public key can (by its nature) be accessed in some way by all participants.

@@

When a voter goes to cast a vote, his/her candidate selection is encrypted locally (i.e., on his/her
computer terminal, in the browser) using ElGamal. Prior to casting the ballot, the voter is
presented with a SHA-1 hash of his/her encrypted ballot. At this point, the voter may choose either
to submit the ballot or to ``audit'' it. In the former case, the ballot is cast and voting is
complete. But when a voter chooses to ``audit,'' he/she is presented with \emph{all} of the data
used to encrypt the vote. Namely, this includes the public key and the ``randomness'' that were used
by an implementation of ElGamal to encrypt the vote. The voter can then -- using a modified ElGamal
(one which allows randomness to be specified) -- perform the encryption and SHA-1 hash him/herself
to verify that the hash that \emph{would} have been cast actually does represent the ballot he/she
intended to cast.

@@

The ``shuffling'' is important because it prevents an attacker (or simple onlooker) from linking
a decrypted ballot with a particular encrypted ballot -- and thus a voter. Re-encryption means that
an auditor examining a proof of proper decryption (see below) cannot determine how a particular
voter cast his/her ballot by hashing all ciphertexts in the proof and matching those hashes to the
publicly-posted encrypted vote hashes.

@@

In Scantegrity, the ballot ``mix'' is predetermined, as it is defined by the generation of Table R.
When that table is constructed, ballots are pseudorandomly ordered. With the exception of audit
ballots, the information revealed that is ultimately revealed allows half of the ballots to be
traced only from Table Q to Table R; and the other half can only be traced from Table R to Table S.
Should Table P be compromised, one could complete all mappings and violate secrecy entirely -- or
simply decrypt encrypted votes with no attention giving to Table R. Should the mapping on
\emph{either} size of Table R (to votes in Table Q or tallies in Table S) be deterministic, privacy
would be compromised for half of all voters.

@@

Helios, which is designed for use in an online setting, has no illusions about coercion: in fact,
the public implementation makes it clear to voters that they would be easy to coerce. Setting
(physical security) aside: as with Scantegrity, Helios does not reveal to a voter all the
information necessary to \emph{prove} a decryption of his/her ballot. Though a voter is able to see
encryption details for ballots chosen for audit, that information is never displayed to the user
when finally casting a ballot. Furthermore, even if it were, it is possible (though perhaps
unlikely) that a crafty voter could fashion encryption details (a false key and false randomization
data) that would produce the same hash but for a different candidate, thus ``proving'' something
untrue to the coercing party. (This is one reason that it is important for the system to use a
collision-resistant hash function.)

@@

Note that each of these systems rely on publication of some information for every ballot that was
cast (whether it be the entire encrypted ballot or a hash of the ballot).

@@

One might wish to prevent a party from determining who did or did not cast \emph{any} ballot.
As we've seen, \term{verifiable counting} typically relies on the ``public'' nature of this data.
Additionally, should this data be hidden, it could potentially be more difficult to notice ``ballot
stuffing'' (discussed above above).

@@

In each of these key systems, there exists some way to tie a vote back to a voter: there is always
some secret. Ideally, there would be a system wherein a vote could be tallied properly (somehow)
without being able to reveal who the vote was for. (Admittedly, that would be difficult: if that is
the only vote, then ``tallying'' just it would reveal the candidate for which it was cast.)

But it would be a worthy goal at least to minimize (if not eliminate) the amount of data that must
be kept secret. Usually it is one or two pieces of data -- and these systems attempt to mitigate
risk by requiring that multiple entities (persons) be present in order to access that secret data.

@@

It is clear that Scantegrity's secrets -- Tables P and R -- are generated using a source of true
randomness. If there is any determinism in generating those tables, an attacker could exploit the
generation method to violate privacy. Helios, on the other hand, was designed with application in
mind and therefore uses standard cryptographic techniques (e.g., ElGamal and SHA-1).

@@

The same can be said for Helios, should it be implemented with inappropriate primitives (not ElGamal
and SHA-1); however, as the authors have designed the scheme with particular primitives in mind, its
specification is less open to interpretation (and thus potentially harmful choices).

>>>>

Once votes have been collected, it is the responsibility of the state to tally votes for the various
candidates in a race and publish \emph{accurate} tallies. Generally, the electorate is reliant on
\emph{someone} to provide these tallies. But it is much less common for voters themselves to have
the opportunity to verify that the votes were tallied \emph{exactly} as they were cast.

@@

While the notions of verifiability presented above allow one to ensure that votes were counted as
they were cast, another problem is to ensure that the body holding the election cannot fabricate
\emph{additional} uncast votes to raise the tallies as it sees fit.

@@

Amidst these other goals, it becomes difficult to prevent \term{coercion}: the ability of some party
to coerce a voter to vote for a particular candidate.

@@

Before an election is held, the election authority must construct four Tables that lie at the core
of the Scantegrity system: Tables P, Q, R, and S.

Some selection of persons associated with the electing body use a secret-sharing scheme to protect a
secret pseudorandom number generator key. Table P lists every ballot that will be produced for the
election and specifies exactly what code is used for each candidate per ballot. These codes are
generated using the pseudorandom generator and \emph{must} be kept secret.

@@

When a ballot has been received, the following takes place:
\begin{enumerate}
	\item
		The candidate code is revealed in Table Q. (If this is an audit ballot -- see below -- then all
		are revealed, and we'll perform the following steps for each code.)
	\item
		A ``check'' is placed on the row in Table R that maps the revealed Q value to some value in S.
	\item
		The Table R mapping is followed into Table S, and a ``check'' is added to a cell in Table R,
		to be counted as a vote for that row's candidate.
\end{enumerate}

@@

Helios \cite{helios} -- unlike Scantegrity and \pv{} -- is an \emph{online} voting
system; however, it, too, is designed with an emphasis on verifiability.

@@

At the heart of Helios is a single ElGamal keypair. The secret key is known only to the Helios
server, but the public key can be accessed in some way by all participants.

@@

When a voter goes to cast a vote, his/her candidate selection is encrypted locally (i.e., on his/her
computer terminal, in the browser) using ElGamal. Prior to casting the ballot, the voter is
presented with a SHA-1 hash of his/her encrypted ballot. At this point, the voter may choose either
to submit the ballot or to ``audit'' it. In the former case, the ballot is cast and voting is
complete. But when a voter chooses to ``audit,'' he/she is presented with \emph{all} of the data
used to encrypt the vote. Namely, this includes the public key and the ``randomness'' that were used
by an implementation of ElGamal to encrypt the vote. The voter can then -- using a modified ElGamal
which allows randomness to be specified -- perform the encryption and SHA-1 hash him/herself
to verify that the hash that \emph{would} have been cast actually does represent the ballot he/she
intended to cast.

@@

The ``shuffling'' is important because it prevents an attacker from linking a decrypted ballot with
a particular encrypted ballot -- and thus a voter. Re-encryption means that an auditor examining a
proof of proper decryption cannot determine how a particular voter cast his/her ballot by hashing
all ciphertexts in the proof and matching those hashes to the publicly-posted encrypted vote hashes.

@@

In Scantegrity, the ballot ``mix'' is predetermined, as it is defined by the generation of Table R.
When that table is constructed, ballots are pseudorandomly ordered. With the exception of audit
ballots, the information revealed that is ultimately revealed allows half of the ballots to be
traced only from Table Q to Table R; and the other half can only be traced from Table R to Table S.
Should Table P be compromised, one could complete all mappings and violate secrecy entirely -- or
simply decrypt encrypted votes with no attention giving to Table R. Should the mapping on
\emph{either} size of Table R to votes in Table Q \emph{or} tallies in Table S be deterministic,
privacy would be compromised for half of all voters.

@@

Helios, which is designed for use in an online setting, has no illusions about coercion: in fact,
the public implementation makes it clear to voters that they would be easy to coerce. Setting
physical security aside: as with Scantegrity, Helios does not reveal to a voter all the
information necessary to \emph{prove} a decryption of his/her ballot. Though a voter is able to see
encryption details for ballots chosen for audit, that information is never displayed to the user
when finally casting a ballot. Furthermore, even if it were, it is possible (though perhaps
unlikely) that a crafty voter could fashion encryption details (a false key and false randomization
data) that would produce the same hash but for a different candidate, thus ``proving'' something
untrue to the coercing party. (This is one reason that it is important for the system to use a
collision-resistant hash function.)

@@

Note that each of these systems rely on publication of some information for every ballot that was
cast -- whether it be the entire encrypted ballot or a hash of the ballot.

@@

One might wish to prevent a party from determining who did or did not cast \emph{any} ballot.
As we've seen, \term{verifiable counting} typically relies on the ``public'' nature of this data.
Additionally, should this data be hidden, it could potentially be more difficult to notice ``ballot
stuffing.''

@@

In each of these key systems, there exists some way to tie a vote back to a voter: there is always
some secret. Ideally, there would be a system wherein a vote could be tallied properly without being
able to reveal who the vote was for.

Admittedly, that would be difficult: if that is the only vote, then ``tallying'' just it would
reveal the candidate for which it was cast. But it would be a worthy goal at least to minimize, if
not eliminate, the amount of data that must be kept secret. Usually it is one or two pieces of data
-- and these systems attempt to mitigate risk by requiring that multiple entities be present in
order to access that secret data.

@@

It is clear that Scantegrity's secrets -- Tables P and R -- are generated using a source of true
randomness. If there is any determinism in generating those tables, an attacker could exploit the
generation method to violate privacy. Helios, on the other hand, was designed with application in
mind and therefore uses standard cryptographic techniques (ElGamal and SHA-1).

@@

The same can be said for Helios, should it be implemented with inappropriate primitives (not ElGamal
and SHA-1); however, as the authors have designed the scheme with particular primitives in mind, its
specification is less open to interpretation and, therefore, potentially harmful choices.
